Verifying Demonstrations

### 2017-08-18 properties.tex
Breaks privacy out of intro (again)
Improves slides for properties

\mode*
\subsection{Verification and privacy}
\label{VerificationAndPrivacy}

@@

\subsubsection{Verification}
\label{Verification}

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.
To have any verifiability, we need the storage (e.g.\ blockchain) to be 
immutable --- i.e.\ it prevents malicious changes.

\begin{frame}<presentation>
  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly (e.g.\ blockchain).
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}
\end{frame}

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{frame}
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}

@@

@@

@@

\begin{frame}<presentation>
  \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify them and then count them.
    \end{itemize}
  \end{idea}
\end{frame}

\subsubsection{Privacy}
\label{Privacy}

@@

  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.

      \item But Alice should not be able to participate twice.

@@

        \item E.g.\ a short-term and a long-term credential, then Alice can 
          drop the short-term credential.
    \end{itemize}
  \end{idea}
\end{frame}

>>>>

\mode*
\section{Verification and privacy}
\label{VerificationAndPrivacy}

@@

\subsection{Verification}
\label{Verification}

@@

If the proofs are stored publicly, then an individual can check that their 
proof has been included there.
Thus \cref{IndividualVerif} is fulfilled.
To have any verifiability, we need the storage to be immutable --- i.e.\ it 
prevents malicious changes.

\begin{frame}<presentation>
  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
    \begin{itemize}
      \item Proofs are stored publicly (e.g.\ anonymous blackboard).
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}
\end{frame}

\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
attacks.
They must also be able to verify that each proof is indeed related to the 
event.
We must associate the proof to the event both spatially (the correct location) 
and temporally (it is related to the time-interval of the event).
We can essentially divide it into the following requirements:
\begin{requirements}[\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}

\begin{frame}<presentation>
  \begin{requirements}[V\ref*{EligibilityVerif}.]
  \item\label{CountOnce} Prove that no individual can be counted more than 
    once.
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
  \item\label{DesignatedEvent} Prove that the data is designated for the event.
\end{requirements}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[Count once]
    \begin{itemize}
      \item Any two proofs by the same individual are linkable.
      \item Includes signature made by a verified key.
    \end{itemize}
  \end{idea}

  \begin{idea}[Designated event]
    \begin{itemize}
      \item Include a protest-specific identifier.
      \item E.g.\ hash of the \enquote{manifesto}.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[Created after start, before end]
    \begin{itemize}
      \item This implies a partially ordered set.
      \item Can be provided by blockchains.
      \item \dots or transactional 
        posets~\cite{BlockchainFreeCryptocurrencies}.
    \end{itemize}
  \end{idea}

  \begin{idea}[At location]
    \begin{itemize}
      \item Use \iac{LP}.
      \item Witnessed (signed) by other participants.
    \end{itemize}
  \end{idea}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
    \begin{itemize}
      \item Proofs are stored publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}

\subsection{Privacy}
\label{Privacy}

@@

  \begin{idea}[P\ref{VotePrivacy} Vote privacy]
    \begin{itemize}
      \item Eve shouldn't be able to link Alice's published proof back to 
        Alice.
      \item But if Alice publishes two proofs, those two are linkable.
      \item We're not interested in unmasking trolls, just not count them more 
        than once.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}<presentation>
  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness (deniability)]
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use 
        it to verify that she participated.

@@

      \item E.g.\ a short-term and a long-term credential, then Alice can 
        drop the short-term credential.

      \item But Alice should still not be able to participate twice.
    \end{itemize}
  \end{idea}
\end{frame}
